\subsubsection{System properties}
We offer Clients an interactive Transaction interface that implements ACID transactions. While all ACID guarantees may be violated by individual byzantine Replicas, the system maintains the illusion of an ACID compliant state to all honest Clients.
Moreover, we guarantee to Clients that the Database is \textit{byzantine Serializable} as defined below. Intuitively this Isolation level guarantees that all honest Clients experience the Database as if there serializable. In order to formally capture this we lay some ground work: \footnote{Defs for commands etc in accordance with BFT DUr. cite}

Let $Op =  \{r, w\} \times K \times V $ and $Dec = \{Commit, \,Abort\}$ be the sets of possible operations and decisions respectively, where $K$ is the set of existing data items (keys) and $V$ the range of possible values. A \textit{request} $req \in (Op \cup Dec) \times C$ maps any such operation or decision to the issuing Client from set $C$. We denote with $Hon \subseteq C$ the subset of honest Clients. 

\textbf{History H.} Informally, a \textit{H} contains the operations (read/write) and decisions (commit/abort) of every transaction issued in the system. Formally, we define a \textit{history H} as a finite sequence of requests.

We define a projection $H|_c$ as the subsequence of requests in $H$ that were issued by Client $c$. A sequence of requests $s = req_i \dots req_{i+t}$ in $H|_c$ form a \textit{Transaction} if $req_i$ is the first request by Client $c$ or $req_{i-1} \in Dec \times c$, and if $req_{i+t} \in Dec \times c$.

We further define:

\textbf{Honest History H(P).} Given protocol P, A \textit{history H} is \textit{honest} if it was generated by participants who all follow P. I.e. concretely, $H(P) \equiv H = H|_{Hon}$.
and

\textbf{Honest-View Equivalent.} A \textit{history H} is honest-view equivalent to a $history H'$ if the Operations and Decisions of all honest Clients are the same and if the final writes are the same.

\textbf{Byz-I} Given a protocol $P$ and an isolation level $I$:
A history H is \textit{byzantine-I} if there exists an honest history \textit{H'} such that H is honest-view equivalent to H' and H' satisfies I. 

Thus, informally a byzantine Isolation level states that the state that honest Clients experience must be explicable by an execution in which all participants were honest.
This definition captures the requirements for any byzantine tolerant protocol that strives to maintain Isolation level I.

We further define some progress properties to limit the influence Byzantine Clients have on system throughput. These will be motiviating factors that we will return to in order to justify our choice of 5f+1 replicas as well as the use of an Optimistic Concurrency Control over a Locking based schema. We later outline an alternative design using 3f+1 replicas that does not maintain this property. 

