\section{Intro-Notes}

\subsection{Header}

 - This paper introduces Indicus\\
 - interactive, scalable DB in the byz fault model\\
 - first to be fully client driven\\
 - therefore: fair and can scale to replica bandwidth/processing limits
 
 \subsection{Context}
 - people/entities would like to share data and/or split replication costs. Keep joint records of relevant data (i.e. for cross Audit): Imagine a transaction clearance between banks  (Libra as example: consortium of parties to manage a currency), a supply chain, different medical providers sharing patient data (for easy migration) - any system where users would like to easily migrate between providers.
 - Parties no longer from the same authority, potentially untrusted. --> byzantine fault tolerance not for increased software failure resistance (bugs etc), but to tolerate some level of misbehavior
 - While BFT was not warranted in single entity replication (extra cost for some more FT), it should be the standard for heterogenous replication. This is the basis for Blockchain where BFT is the norm.
 
 -
 - SMR powerful fault tolerant technique. Creates illusion of single Database, thus simplifying application design. Replication is masked.\\
 
 
 - Goal: Make BFT accessible to the mainstream. Requires scalability and low latency. Cost needs to be tolerable - more reasonable if replication is done as consortium (each party pays for subset).
 

\subsection{Existing systems shortcomings}
- systems were designed for different assumptions: single authority low replication vs high replication degree in a consoritum of untrusted parties\\
- non-interactive transactions\\
- totally ordered\\
- leader based: fairness and scalability bottleneck \\
- Crash Failure model\\
- single sharded\\

\subsection{Key insights}
- ?? \\
- implicit partial order suffices \\
- put clients in charge: responsible for their own liveness;  standard way to scale a system\\
- do single slot binary consensus\\
-
\paragraph{Challenge} Empowering byzantine Clients is complicated and dangerous

\subsection{Positive Implications of Insight/Design}
- robust to censorship and frontrunning (if network not adversarial) as there exist no central authority \\
-  allows commutative/non-conflicting Transactions to both be executed and validated out of order, thus maximizing parallelism. \\
-  minimizes the state, communication and computation load on replicas, as Clients serve as both execution hub and broadcast channel for their own Transactions. \\
- As any Quorum system, Indicus is inherently load-balanced as there exists no leader bottleneck and all replicas have equal responsibility\\
- In Indicus liveness is a client local property. Unlike SMR, where the entire system halts during view changes, Byzantine participants may stall system progress only for the objects their transactions touch. Hence, the system appears live to any non-conflicting Transaction


\subsection{Results discussion}
- latency should not be that much higher compared to Tapir\\
- throughput better than an atomic broadcast version\\
- abort rate doesnt rise too fast; mvtso improves abort rater over OCC (if not, then its useless overhead and we can use OCC)


\subsection{Limitations}
 - Like any speculative system, Indicus is vulnerable to high contention in which case it needs to resort to aborts\\
 - This can especially be exploited by byzantine participants if the network is adversarial.\\
 - 

\subsection{Contribution summary}
 - Present definitions for what it means to provide ACID (specifically Isolation) guarantees in a byzantine setting\\
 - We present design, implementation and evaluation of Indicus, a fully client-driven BFT ACID transactional system \\
 - Design of a leaderless, client-driven execution and replication protocol that does not enforce a total order\\
 - The design of a more aggressive optimistic concurrency control scheme that is robust to byzantine behaviors
 